Assessing primitives performance\\ on multi-stage execution

### 2018-05-08 paper.tex
proper plots for bench results

taille 0

\begin{tikzpicture}
  \begin{axis}
  [
boxplot/draw direction
=y,
    xtick={1,2,3},
    xticklabels={Plugin, Slang, Slang+JIT},
    ]
    \addplot+[
    boxplot prepared={
      median=2.942,
      upper quartile=2.977,
      lower quartile=2.911,
      upper whisker=3.098,
      lower whisker=2.797
    },
    ] coordinates {};
    \addplot+[
    boxplot prepared={
      median=0.9594,
      upper quartile=0.9791,
      lower quartile=0.9230,
      upper whisker=1.1059,
      lower whisker=0.8705
    },
    ] coordinates {};
    \addplot+[
    boxplot prepared={
      median=0.4258,
      upper quartile=0.4310,
      lower quartile=0.4227,
      upper whisker=0.5181,
      lower whisker=0.4074
    },
    ] coordinates {};
  \end{axis}
\end{tikzpicture}

taille 5

\begin{tikzpicture}
  \begin{axis}
  [
boxplot/draw direction=y,
    xtick={1,2,3},
    xticklabels={Plugin, Slang, Slang+JIT},
    ]
    \addplot+[
    boxplot prepared={
      median=0.6904,
      upper quartile=0.6998,
      lower quartile=0.6835,
      upper whisker=0.7353,
      lower whisker=0.6407
    },
    ] coordinates {};
    \addplot+[
    boxplot prepared={
      median=0.2530,
      upper quartile=0.2594,
      lower quartile=0.2449,
      upper whisker=0.2836,
      lower whisker=0.2323
    },
    ] coordinates {};
    \addplot+[
    boxplot prepared={
      median=0.1455,
      upper quartile=0.1475,
      lower quartile=0.1425,
      upper whisker=0.1636,
      lower whisker=0.1266
    },
    ] coordinates {};
  \end{axis}
\end{tikzpicture}

taille 100
\begin{tikzpicture}
  \begin{axis}
  [
boxplot/draw direction=y,
    xtick={1,2,3},
    xticklabels={Plugin, Slang, Slang+JIT},
    ]
    \addplot+[
    boxplot prepared={
      median=0.10378,
      upper quartile=0.10435,
      lower quartile=0.10355,
      upper whisker=0.10586,
      lower whisker=0.09964
    },
    ] coordinates {};
    \addplot+[
    boxplot prepared={
      median=0.05689,
      upper quartile=0.05706,
      lower quartile=0.05648,
      upper whisker=0.05985,
      lower whisker=0.05527
    },
    ] coordinates {};
    \addplot+[
    boxplot prepared={
      median=0.05564,
      upper quartile=0.05560,
      lower quartile=0.05552,
      upper whisker=0.05985,
      lower whisker=0.05382
    },
    ] coordinates {};
  \end{axis}
\end{tikzpicture}

taille 10000
\begin{tikzpicture}
  \begin{axis}
  [
boxplot/draw direction
=y,
    xtick={1,2,3, 4},
    xticklabels={Baseline, Plugin, Slang, Slang+JIT},
    ]
    \addplot+[
    boxplot prepared={
      median=10474,
      upper quartile=10506,
      lower quartile=10455,
      upper whisker=11905,
      lower whisker=10099
    },
    ] coordinates {};
    \addplot+[
    boxplot prepared={
      median=761,
      upper quartile=761,
      lower quartile=761,
      upper whisker=765,
      lower whisker=760
    },
    ] coordinates {};
    \addplot+[
    boxplot prepared={
      median=476.7,
      upper quartile=477,
      lower quartile=476,
      upper whisker=482,
      lower whisker=475
    },
    ] coordinates {};
    \addplot+[
    boxplot prepared={
      median=500,
      upper quartile=501.8,
      lower quartile=500,
      upper whisker=512,
      lower whisker=499
    },
    ] coordinates {};
  \end{axis}
\end{tikzpicture}

>>>>

\cba{Personnellement je ferais une figure, ou tu places tes graphes dedans, et pares tu referes a la figure dans le texte.}

\begin{figure*}
  \centering

    \begin{subfigure}[b]{.45\textwidth}

    \begin{tikzpicture}
      \begin{axis}
      [
        xtick={1,...,5},
        xticklabels={Baseline, oldPlugin, SlangPlugin, PureSlang, Slang+JIT},
        %x tick label as interval,
        font={\tiny},
		ybar=10pt,
		xbar width=0.30,
		no markers,Baseline/.style={red},2/.style={green},3/.style={blue}
		%cycle list={red, orange, green, purple, black}
        ]
\addplot[
    fill=black!25,
    %draw=none,
    %fill,
    draw=black,
    fill,
    point meta=y,
    every node near coord/.style={inner ysep=5pt},
    error bars/.cd,
        y dir=both,
        y explicit
]  
table [y error=error] {
x   y           error    
1   1           0 
2   0.3147064   0.002288488 
3   0.3035965   0.001786185
4   0.8545431   0.006132950 
5   2.250732    0.04133638 
};            
      \end{axis}
    \end{tikzpicture}
    \subcaption{Size 0}
    \end{subfigure}
    \begin{subfigure}[b]{.45\textwidth}
    \begin{tikzpicture}
      \begin{axis}
      [
        xtick={1,...,5},
        xticklabels={Baseline, oldPlugin, SlangPlugin, PureSlang, Slang+JIT},
        %x tick label as interval,
        font={\tiny},
		ybar=10pt,
		xbar width=0.30
        ]
\addplot[
    fill=black!25,
    draw=black,
    point meta=y,
    every node near coord/.style={inner ysep=5pt},
    error bars/.cd,
        y dir=both,
        y explicit
] 
table [y error=error] {
x   y           error    
1   1           0 
2   1.2505193   0.004611354 
3   1.2295801   0.001810171
4   2.8205415   0.008035024 
5   7.089806    0.01403785 
};            
      \end{axis}
    \end{tikzpicture}

    \subcaption{Size 5}
    \end{subfigure}
    \begin{subfigure}[b]{.45\textwidth}
 \begin{tikzpicture}
      \begin{axis}
      [
        xtick={1,...,5},
        xticklabels={Baseline, oldPlugin, SlangPlugin, PureSlang, Slang+JIT},
        %x tick label as interval,
        font={\tiny},
		ybar=10pt,
		ymin=0,
		xbar width=0.30
        ]
\addplot[
    fill=black!25,
    draw=black,
    point meta=y,
    every node near coord/.style={inner ysep=5pt},
    error bars/.cd,
        y dir=both,
        y explicit
] 
table [y error=error] {
x   y           error    
1   1           0 
2   6.6951738   0.062391122 
3   6.6032572   0.024774416
4   10.3029394   0.061481532 
5   17.979611    0.10127936 
};            
      \end{axis}
    \end{tikzpicture}

    \subcaption{Size 100}
    \end{subfigure}
    \begin{subfigure}[b]{.45\textwidth}

     \begin{tikzpicture}
      \begin{axis}
      [
        xtick={1,...,5},
        xticklabels={Baseline, oldPlugin, SlangPlugin, PureSlang, Slang+JIT},
        %x tick label as interval,
        font={\tiny},
		ybar=10pt,
		ymin=0,
		xbar width=0.30
        ]
\addplot[
    fill=black!25,
    draw=black,
    point meta=y,
    every node near coord/.style={inner ysep=5pt},
    error bars/.cd,
        y dir=both,
        y explicit
] 
table [y error=error] {
x   y           error    
1   1           0 
2   9.4064534   0.036698187 
3   9.2138415   0.013982843
4   13.4384830   0.040202717 
5   26.404792    0.09298324 
};            
      \end{axis}
    \end{tikzpicture}

   \subcaption{Size 1000}
   \end{subfigure}
   \caption{GCC-Linux results}
\end{figure*}

\begin{figure*}
  \centering

    \begin{subfigure}[b]{.45\textwidth}

    \begin{tikzpicture}
      \begin{axis}
      [
        xtick={1,...,5},
        xticklabels={Baseline, oldPlugin, SlangPlugin, PureSlang, Slang+JIT},
        %x tick label as interval,
        font={\tiny},
		ybar=10pt,
		ymin=0,
		xbar width=0.30
        ]
\addplot[
    fill=black!25,
    draw=black,
    point meta=y,
    every node near coord/.style={inner ysep=5pt},
    error bars/.cd,
        y dir=both,
        y explicit
] 
table [y error=error] {
x   y           error    
1   1           0 
2   0.3147064   0.002288488 
3   0.3035965   0.001786185
4   0.8545431   0.006132950 
5   2.250732    0.04133638 
};            
      \end{axis}
    \end{tikzpicture}

    \subcaption{Size 0}
    \end{subfigure}
    \begin{subfigure}[b]{.45\textwidth}

    \begin{tikzpicture}
      \begin{axis}
      [
        xtick={1,...,5},
        xticklabels={Baseline, oldPlugin, SlangPlugin, PureSlang, Slang+JIT},
        %x tick label as interval,
        font={\tiny},
		ybar=10pt,
		xbar width=0.30
        ]
\addplot[
    fill=black!25,
    draw=black,
    point meta=y,
    every node near coord/.style={inner ysep=5pt},
    error bars/.cd,
        y dir=both,
        y explicit
] 
table [y error=error] {
x   y           error    
1   1           0 
2   1.2505193   0.004611354 
3   1.2295801   0.001810171
4   2.8205415   0.008035024 
5   7.089806    0.01403785 
};            
      \end{axis}
    \end{tikzpicture}
    \subcaption{Size 5}
    \end{subfigure}
    \begin{subfigure}[b]{.45\textwidth}
 \begin{tikzpicture}
      \begin{axis}
      [
        xtick={1,...,5},
        xticklabels={Baseline, oldPlugin, SlangPlugin, PureSlang, Slang+JIT},
        %x tick label as interval,
        font={\tiny},
		ybar=10pt,
		ymin=0,
		xbar width=0.30
        ]
\addplot[
    fill=black!25,
    draw=black,
    point meta=y,
    every node near coord/.style={inner ysep=5pt},
    error bars/.cd,
        y dir=both,
        y explicit
] 
table [y error=error] {
x   y           error    
1   1           0 
2   6.6951738   0.062391122 
3   6.6032572   0.024774416
4   10.3029394  0.061481532 
5   17.979611   0.10127936 
};            
      \end{axis}
    \end{tikzpicture}
    \subcaption{Size 100}
    \end{subfigure}
    \begin{subfigure}[b]{.45\textwidth}

    \begin{tikzpicture}
      \begin{axis}
      [
        xtick={1,...,5},
        xticklabels={Baseline, oldPlugin, SlangPlugin, PureSlang, Slang+JIT},
        %x tick label as interval,
        font={\tiny},
		ybar=10pt,
		ymin=0,
		xbar width=0.30
        ]
\addplot[
    fill=black!25,
    draw=black,
    point meta=y,
    every node near coord/.style={inner ysep=5pt},
    error bars/.cd,
        y dir=both,
        y explicit
] 
table [y error=error] {
x   y           error    
1   1           0 
2   9.4064534   0.036698187 
3   9.2138415   0.013982843
4   13.4384830  0.040202717 
5   26.404792   0.09298324 
};            
      \end{axis}
    \end{tikzpicture}

   \subcaption{Size 1000}
   \end{subfigure}
   \caption{LLVM-Mac results}
\end{figure*}
